Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-15 hscc2017/paper.tex
wording

Modern implementations of embedded control systems have proliferated with
the availability of low-cost devices that can perform highly non-trivial
control tasks, with significant impact in numerous application areas such as
environmental control and robotics~\cite{astrom1997computer, Franklin15}. 
Correct control is non-trivial, however.  The problem is exacerbated by
artefacts specific to digital control, such as the effects of
finite-precision arithmetic, time discretization, and quantization noise
introduced by A/D and D/A conversion.  Thus, programming expertise is a key
barrier to broad adoption of correct digital controllers, and requires
considerable knowledge often unusual to the control engineer.

Beyond classical a-posteriori validation procedures in digital control,
there has been plenty of previous work aiming at \emph{verifying} a given
designed controller, which however broadly lack automation.  Recent work has
studied the stability of digital controllers considering implementation
aspects, i.e., fixed-point arithmetic and the word length~\cite{Bessa16}. 
They exploit advances in bit-accurate verification of C programs to obtain a
verifier for software-implemented digital control.

>>>>

Modern implementations of embedded control systems have proliferated with
the availability of low-cost devices that can perform highly non-trivial
control tasks, with significant impact in numerous application areas such as
environmental control and robotics~\cite{astrom1997computer, Franklin15}. 
Correct control is non-trivial, however.  The problem is exacerbated by
artefacts specific to digital control, such as the effects of
finite-precision arithmetic, time discretization, and quantization noise
introduced by A/D and D/A conversion.  Thus, programming expertise is a key
barrier to broad adoption of correct digital controllers, and requires
considerable knowledge outside of the expertise of many control engineers.

Beyond classical a-posteriori validation in digital control, there has been
plenty of previous work aiming at \emph{verifying} a given designed
controller, which however broadly lack automation.  Recent work has studied
the stability of digital controllers considering implementation aspects,
i.e., fixed-point arithmetic and the word length~\cite{Bessa16}.  They
exploit advances in bit-accurate verification of C programs to obtain a
verifier for software-implemented digital control.
